### 2019-03-15 draft_charts.Rmd
Update charts outline.

```{r}
read_csv("data/figure10.csv") %>%
  filter(doby <= 1985) %>%
  mutate(doby = case_when(
    doby <= 1945 ~ "1936-1945",
    doby <= 1955 ~ "1946-1955",
    doby <= 1965 ~ "1956-1965",
    doby <= 1975 ~ "1966-1975",
    doby <= 1985 ~ "1976-1985")
  ) %>% 
  ggplot(aes(x = lifetime_earn, y = slifetime_earn)) +
  geom_point(alpha = 0.05) +
  geom_smooth(method = "lm", formula = y ~ x - 1) +
  scale_x_continuous(expand = c(0, 0.05), 
                     limits = c(0, 10000000),
                     breaks = c(0, 5000000, 10000000),
                     labels = scales::dollar) +
  scale_y_continuous(expand = c(0, 0.05), 
                     limits = c(0, 10000000),
                     breaks = c(0, 5000000, 10000000),
                     labels = scales::dollar) +
  facet_wrap(~doby) +
  labs(
    title = "Wive's lifetime earnings vs. husband's lifetime earnings",
    subtitle = "Amongst married couples",
    x = "Wife's lifetime earnings",
    y = "Husband's lifetime earnings"
  ) +
  scatter_grid()

>>>>

```{r}
read_csv("data/figure10.csv") %>%
  filter(doby <= 1985) %>%
  mutate(doby = case_when(
    doby <= 1945 ~ "1936-1945",
    doby <= 1955 ~ "1946-1955",
    doby <= 1965 ~ "1956-1965",
    doby <= 1975 ~ "1966-1975",
    doby <= 1985 ~ "1976-1985")
  ) %>% 
  ggplot(aes(x = lifetime_earn, y = slifetime_earn)) +
  geom_point(alpha = 0.05) +
  geom_smooth(method = "lm", formula = y ~ x - 1) +
  scale_x_continuous(expand = c(0, 0.05), 
                     limits = c(0, 10000000),
                     breaks = c(0, 5000000, 10000000),
                     labels = scales::dollar) +
  scale_y_continuous(expand = c(0, 0.05), 
                     limits = c(0, 10000000),
                     breaks = c(0, 5000000, 10000000),
                     labels = scales::dollar) +
  facet_wrap(~doby) +
  labs(
    title = "Wife's lifetime earnings vs. husband's lifetime earnings",
    subtitle = "Amongst married couples",
    x = "Wife's lifetime earnings",
    y = "Husband's lifetime earnings"
  ) +
  scatter_grid()
